Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-06-26 parallel-tractability-J-v9/response2.tex
revised response

Algorithm~$\mathsf{A}_{\text{opt}}$ also works on the parallel condition.
That is, each processor $p$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
and processor $p$ can access the locations of nodes $B_1,\ldots,B_n, H$ in constant time.
In order to compute $S_{\!\textit{\tiny rch}}$, processor $p$ should check the derivability
of nodes $B_1,\ldots,B_n, H$. If only node $B_i$ ($i\in\{1,\ldots n\}$) and node $H$
are still not derived, then processor $p$ creates a pair $(B_i, H)$ in $S_{\!\textit{\tiny rch}}$.
The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
Under the parallel condition, the above procedure uses constant time as well as checking
the applicability of a rule instantiation. \textcolor{red}{BG: I
  cannot parse the previous sentence, in particular the `as well as
  checking\ldots' part.}
We have added the above arguments \textcolor{red}{to the paper?} to
make the claim that the computation of $S_\text{rch}$ costs
constant time clearer.
The procedure of updating $G$ is similar to that of Algorithm~$\mathsf{A}_{\text{bsc}}$.

>>>>

Algorithm~$\mathsf{A}_{\text{opt}}$ also works on the parallel condition.
That is, each processor $p$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
and processor $p$ can access the locations of nodes $B_1,\ldots,B_n, H$ in constant time.
In order to compute $S_{\!\textit{\tiny rch}}$, processor $p$ should check the derivability
of nodes $B_1,\ldots,B_n, H$. If only node $B_i$ ($i\in\{1,\ldots n\}$) and node $H$
are still not derived, then processor $p$ creates a pair $(B_i, H)$ in $S_{\!\textit{\tiny rch}}$.
The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
The main work of the above procedure is to check the derivability
of the nodes in the processed rule instantiation, which is the same as that of
checking the applicability of the rule instantiation.
Under the parallel condition, the above procedure also uses constant time.
We have added the above arguments to the paper to
make the claim that the computation of $S_\text{rch}$ costs
constant time clearer.
The procedure of updating $G$ is similar to that of Algorithm~$\mathsf{A}_{\text{bsc}}$.
